Do Restaurants in A study of relationship between neighbourhood income and DineSafe infractions

### 2024-01-23 outputs/paper/paper.qmd
ADD llm usage, add weakness draft

As we look at different infraction severities however, it seems like the east side of the city causes more severe infraction compared to the west side. One could interpret this as the wards in the east side causes less infractions, but each infractions are more severe in the east.

@@

Weaknesses and next steps should also be included.

>>>>

As we look at different infraction severities however, it seems like the east side of the city causes more severe infraction compared to the west side. One could interpret this as the wards in the east side causing less infractions in numbers, but each infractions are more severe in the east.

@@

Dinesafe inspections are done by numerous inspectors, and different inspectors will be better at pointing out infraction than others. This means using Dinesafe infractions to decide which restaurants are the cleanest, and which wards have the cleanest restaurants may not be the most appropriate. Not only that, there can be a seasonal difference too. For example, mice infestations are the most common during fall and winter season [TODO: ADD SOURCE HERE]. Meaning if an inspection was done in fall or winter rather than spring or summer, an establishment might have a higher chance of getting caught with mice infestation. Having any kind of mice infestation leads to a closed notice, as it is a crucial infraction [TODO: Add archive.org page about this].
